For Laura

### 2018-04-05 Laura_pres.Rmd
Moving over from GitLab repo, all files

- Based on PCA on correlation matrix of ranked institutional data
- Two Scales: Aggregate (x-axis) and Per-Capita (y-axis)
- Three categories of PhD-granting institutions: R1 to R3

>>>>

- Based on PCA on correlation matrix of ranked institutional data
- Two Scales: Aggregate (x-axis) and Per-Capita (y-axis)
-u Three categories of PhD-granting institutions: R1 to R3

### 2018-04-05 analysis/SEMwriteup.Rmd
Moving over from GitLab repo, all files

In a traditional SEM model, the manifors

@@

## A First Model

## Changing Priors

## Sensitivity to Priors

##Bayesian SEM - Some Conclusions

@@

ggplot(Score_dist) + geom_point(aes(x = Aggregate, y = PerCap, color = CCScores_r_cov$rate_2015))
```

>>>>

@@

## A First Model
The first model considered was the bayesian SEM with no additional changes made to the code. The estimates were quite different from those calculated in the original SEM. We looked into the priors and saw that some of them were pretty highly informative. 
```{r}
require(blavaan)
bsem_norm <- blavaan::bsem(model2, data=cc2015_r, cp='srs', std.lev=TRUE, convergence='auto', dp=dpriors())
summary(bsem_norm)
```

## Changing Priors
The highly informative priors should have shrunk the estimators a little too much, so we decided to try some normal priors with large variance terms (in order to not be so informative). Since the latent variables are assumed in a frequentist setting to be multivariate normals, we assumed that normal priors with large variances would be uninformative and thus reasonable. However, using them gave us even more shrunk estimates compared to the frequentist SEM. 
```{r}
bNORM <- blavaan::bsem(model2, data=cc2015_r, cp='srs', std.lv=TRUE, convergence='auto', dp=dpriors(lambda="dnorm(0,10000)"))
summary(bNORM) #lambda
```

## Sensitivity to Priors
As of now, the sensitivity of the prior choice is a problem. We want fairly stable estimates and the Blavaan method is  not giving us something particularly useful.

Moreover, Blavaan kicks the estimation of posteriors out to JAGS, and occasionally convergence issues have been a problem. It may be better to think about coding out a Bayesian version of SEM by ourselves rather than fitting the SEM using a package.

@@

ggplot(Score_dist) + geom_point(aes(x = Aggregate, y = PerCap, color = cc2015_new$BASIC2015))
```

### 2018-04-05 for_laura.Rmd
Moving over from GitLab repo, all files

---
title: "SEM Code"
author: "Paul"
date: "March 6, 2018"
output: pdf_document
---

@@

##Correlation Plot
We used the correlation plot below to inform the two latent factors that we are using.

```{r}
setwd("~/Carnegie-SEM/data")
cc2015 <- read.csv("CC2015data.csv",header = TRUE)

@@

##SEM Code:

The SEM fit below on the STEM and Non-STEM latent factors is given with the following code.

```{r}
model4 <- '
HUMANITIES=~HUM_RSD+OTHER_RSD+SOCSC_RSD+NONS.ER.D+FACNUM
STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D+FACNUM
Aggregate=~HUMANITIES+STEM'

@@

>>>>

---
title: "For Laura"
author: "Paul Harmon and Sarah McKnight"
date: "December 11, 2017"
output: pdf_document
---

@@

We generated a new SEM model for the Carnegie Data in order to get things to run efficiently. The code for generating the model and reading in the dataset is given below.

```{r}
#read in data
setwd("~/Carnegie-SEM/data")
cc2015 <- read.csv("CC2015data.csv",header = TRUE)

@@

Based on the inability of the previous model to generate a positive-definite variance covariance matrix, we looked back at the model and determined that things are too highly correlated to get things to work. Rather than modeling the Aggregate and Per-Capita traits from the same set of variables, we decided to look at STEM vs. Non-STEM differences. This allowed us to have two correlated factors, but they did not depend on the same variables so we were able to get results that looked reasonable.

The model fit is below: 
```{r}
model4 <- '
HUMANITIES=~HUM_RSD+OTHER_RSD+SOCSC_RSD+NONS.ER.D+FACNUM
STEM=~STEM_RSD+PDNFRSTAFF+S.ER.D+FACNUM
Aggregate=~HUMANITIES+STEM'

@@

The model would look like the following, in a path diagram:

```{r}
library(semPlot)
semPaths(lavaan_sem_new)
```

Finally, we can generate a plot of the factors plotted against each other: 
```{r}
library(ggplot2)
CCScores_r_cov_new <- as.data.frame(lavaan::predict(lavaan_sem_new))
names(CCScores_r_cov_new)
    #creates a plot and colors by Carnegie Classification Colors  
  ggplot(CCScores_r_cov_new) + geom_point(aes(x = STEM, y = HUMANITIES), color = "gray30", symbol = "gray30")+ 
   ggtitle("Predicted vs Actual Classifications") + theme_bw() + coord_fixed(ratio = 1)
```
